---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autodep

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/JSzitas/autodep/workflows/R-CMD-check/badge.svg)](https://github.com/JSzitas/autodep/actions)
[![Codecov test coverage](https://codecov.io/gh/JSzitas/autodep/branch/main/graph/badge.svg)](https://codecov.io/gh/JSzitas/autodep?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/autodep)](https://CRAN.R-project.org/package=autodep)
<!-- badges: end -->

**autodep** scans a package /R directory and finds all valid dependencies of the form namespace::object. 
These are then rendered as roygen tags in the /R directory (so they are easy to read) and the appropriate 
packages are written to the description file (into the **Imports** section). 


## Installation 

Install easily from github via: 
```{r, eval = FALSE}
devtools::install_github("JSzitas/autodep")
```


## Usage

Use **autodep** to automatically convert namespace::function calls to roxygen tags, 
and register the required packages in the description file. 

```{r, eval =FALSE}
autodep(path = ".", overwrite = TRUE, roxygen_file_name = "R/package_imports.R")
```

You just need to set the path to the package (via **path**), specify **overwrite = TRUE** 
(in case you have previously used autodep and wish to upgrade the imports) and give it 
the name of the file to write the roxygen tags to - by default **"R/package_imports.R"** 

Note that the roxygen tags should always be placed in the **/R** project/package sub-directory.



